---
output:
  md_document:
    variant: gfm
html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%",
    message = FALSE,
    warning = FALSE
)
```

```{r echo=FALSE, results="hide", message=FALSE}
library("badger")
```

# yyeasy: Easily draw sectors with grid and ggplot2

<!-- badges: start -->
[![Project Status: Active - The project has reached a stable, usable state and is being actively developed.](http://www.repostatus.org/badges/latest/active.svg)](http://www.repostatus.org/#active)
<!-- [![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/yyeasy)](https://cran.r-project.org/package=yyeasy) -->
`r badge_devel("yanpd01/yyeasy", "green")`

<!-- `r badger::badge_custom("platforms", "all", "green")` -->
`r badger::badge_custom("Windows", "passing", "green")`
`r badger::badge_custom("Linux", "passing", "green")`
<!-- badges: end -->

```{r comment="", echo=FALSE, results='asis'}
cat(packageDescription("yyeasy")$Description)
```

## :writing_hand: Authors

Pengdong Yan



## :arrow_double_down: Installation



Get the development version from github or gitee:

```{r, eval = FALSE}
## install.packages("remotes")
# from github
remotes::install_github("yanpd01/yyeasy")
# from gitee
remotes::install_git("https://gitee.com/yanpd01/yyeasy")
```


##  :books: Usage

For the usage of this R package, please type `?function` after installation to view it.
There are detailed case descriptions in it.
